---
title: Example Bug
format: html
---

I would like to demonstrate how to create R, Python, and Julia code chunks in a document.

In the past I have used 4 back ticks to capture what an R code chunk looks like:

````

```{r}
# some R code
image(volcano)
```

````

However this doesn't seem to work.

Is the current way to use the `verbatim` approach like so:

````{verbatim, lang = "r"}

```{r}
# some R code
image(volcano)
```

````

So instead of the following:

::: {.panel-tabset}

## R

````
```{r}
#| label: r-chunk-name
# a code chunk
```
````

## python

````
```{python}
#| label: py-chunk-name
# a code chunk
```
````

## julia

````
```{julia}
#| label: julia-chunk-name
# a code chunk
```
````

::: 

I would need to do

::: {.panel-tabset}

## R

````{verbatim, lang = "r"}
```{r}
#| label: r-chunk-name
# a code chunk
```
````

## python

````{verbatim, lang = "python"}
```{python}
#| label: py-chunk-name
# a code chunk
```
````

## julia

````{verbatim, lang = "julia"}
```{julia}
#| label: julia-chunk-name
# a code chunk
```
````

::: 
